---
title: "101 Database Automation Task"
author: "Justin Lim"
output: html_document
runtime: shiny
---

## Database Automation Task

```{r setup, message=FALSE, warning = FALSE, echo = FALSE}
library(formattable)
library(tidyverse)
library(RSQLite)
library(shiny)
```

```{r, warning = FALSE, echo = FALSE}
insert_query = function(con, name, geog_pref, stage_pref, sector_pref){
        insert_qry = paste0('INSERT INTO investors(Name, Geography, Stage, Sector) VALUES ("'  ,  name,  '", "'  ,geog_pref, '", "'  ,stage_pref, '", "',  sector_pref, '");' )
        dbExecute(con, insert_qry)
        investors <- tbl(con, "investors")
        investors = investors %>% collect()
        dbDisconnect(con)
        return(investors)
      }

shiny_VC_matching = function(){
  con <- dbConnect(SQLite(), "data/companies.db")
  companies <- tbl(con, "companies")
  investors <- tbl(con, "investors")
  companies = companies %>% collect()
  investors = investors %>% collect()
  reactive_table <- reactiveValues(data = investors)
  dbDisconnect(con)
  
  geog_choices = companies %>% 
    add_row(Geography = "No Preference") %>% 
    select(Geography)
  
  sector_choices = companies %>% 
    add_row(Sector = "No Preference") %>% 
    select(Sector)
  
  stage_choices = companies %>% 
    add_row(Stage = "No Preference") %>% 
    select(Stage)
  
  shinyApp(
    ui = fluidPage(
      titlePanel("Database"),
      sidebarLayout(
        sidebarPanel = sidebarPanel(
        width = 3,
        selectInput("user", h4("User profile"), choices = investors$Name),
        actionButton("setup_modal", "Create new profile"),
        selectInput("geog", h4("Geography"), choices = geog_choices),
        selectInput("sector", h4("Sector"), choices = sector_choices),
        selectInput("stage", h4("Stage"), choices = stage_choices),
        actionButton("run", "Generate table"),
        checkboxInput("checkbox", 
                      label = "Generate detailed table", 
                      value = FALSE),
        checkboxInput("filter_geog", 
                      label = "Filter by Geography", 
                      value = TRUE),
        checkboxInput("filter_sector", 
                      label = "Filter by Sector", 
                      value = TRUE),
        checkboxInput("filter_stage", 
                      label = "Filter by Financial Stage", 
                      value = TRUE)
      ),
      mainPanel = mainPanel(
        h4("List of companies:"),
        dataTableOutput("table")
      )
      )
    ),
    
    server = function(input, output, session) {
      
      observeEvent(input$setup_modal, {
            showModal(modalDialog(
              textInput("name", h4("User Name")),
              selectInput("geog_pref", h4("Geography preference"), choices = (companies %>% add_row(Geography = "No Preference"))$Geography, selected = "No Preference"), 
              selectInput("sector_pref", h4("Sector preference"), choices = (companies %>% add_row(Sector = "No Preference"))$Sector, selected = "No Preference"),
              selectInput("stage_pref", h4("Stage preference"), choices = (companies %>% add_row(Stage = "No Preference"))$Stage, selected = "No Preference"),
              actionButton("create", "Create profile"),
              textOutput("errorcheck"),
              easyClose = TRUE,
              footer = tagList(
              actionButton("close", "Close"))
              )
              )
          })
      
      observeEvent(input$create, {
          con <- dbConnect(SQLite(), "data/companies.db")        
          safeGet = safely(insert_query)
          safeTester = safeGet(
            con,
            input$name,
            input$geog_pref,
            input$stage_pref,
            input$sector_pref
          ) 
          results_error = safeTester$error
          reactive_table$data = safeTester$result
          if (is.null(results_error) == FALSE & input$name %in% reactive_table$data$Name) {
              output$errorcheck = renderUI(stop("Please choose another name"))
          }
          else if (is.null(results_error) == FALSE) {
              output$errorcheck = renderUI(stop(results_error$message))
          }
          if (is.null(results_error)){
            output$errorcheck = renderText("No error found")
            updateSelectInput(session, "user", choices = reactive_table$data$Name)
            removeModal()
          }
        })
      observeEvent(input$close, {
            removeModal()
        })
      
      
      observeEvent(input$user, {
        if (input$user != ""){
          selected_name = toString(input$user)
          updateSelectInput(session, "geog", choices = geog_choices, 
                            selected = as.character(reactive_table$data %>% filter(Name==selected_name) %>% select(Geography)))
          updateSelectInput(session, "sector", choices = sector_choices,
                            selected = as.character(reactive_table$data %>% filter(Name == selected_name) %>% select(Sector)))
          updateSelectInput(session, "stage", choices = stage_choices, 
                            selected = as.character(reactive_table$data %>% filter(Name == selected_name) %>% select(Stage)))
          output$table2 = renderDataTable({ reactive_table$data
            })
        }
        })
      
      output$table = renderDataTable({
        
        if (!input$checkbox) {
          companies = companies %>% 
            select(`Company Name`, Geography, Stage, Sector,`Valuation ($B)`, `Total Raised ($B)`)
        }
        
        if (input$filter_geog & input$geog != "No Preference" ){
          companies = companies %>%
          filter(Geography == input$geog)
        }
        if (input$filter_sector & input$sector != "No Preference" ){
          companies = companies %>%
          filter(Sector == input$sector)
        }
        if (input$filter_stage & input$stage != "No Preference" ){
          companies = companies %>%
          filter(Stage == input$stage)
        }
        else{
          companies
        }
        
      }) %>% 
        bindEvent(input$run)
    },
    options = list(height = 800)
    )
}
```

```{r, warning = FALSE, message=FALSE}
shiny_VC_matching()
```

### Description:

This shiny app matches startups, stored in an sqlite database, to a users' preferences. The app also allows users to create new profiles and specify their preferences, which are also stored in the database. 

A user can create a user profile, along with their preferences, and use these preferences to find matching startups in the database. The user can modify these search queries using the dropdown tables in the app and generate more detailed statistics as well. Within the table, the startups can be sorted based on each column. 

### Github link:
https://github.com/JustinLimrh/101-db

### References:
https://shiny.rstudio.com/  
https://stackoverflow.com/questions/68707587/in-r-shiny-how-to-render-a-reactive-data-table  
https://data.library.virginia.edu/creating-a-sqlite-database-for-use-with-r/  


